---
title: "R Project 1 - Hello R"
author: "Eduardo Guzman"
date: "9/16/2020"
output: 
  html_document: 
    highlight: tango
    theme: cosmo
    fig_width: 8
    fig_height: 8
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

There are 1846 rows in "datasaurus_dozen", 3 columns, and 3 variables (dataset, x, y).

### Exercise 2

The correlation coefficient for the "dino_data" dataset is: -0.0645.

First let's plot the data in the dino dataset:

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

The correlation coefficient for the "star_data" is: -0.0630. This is roughly a .0015 difference from the "dino_data" correlation coefficient.

Plot of the star dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
    geom_point()
```

And the calculated correlation coefficient:
  
```{r cor-star}
star_data %>%
  summarize(r = cor(x,y))
```

### Exercise 4

The correlation coefficient for the "circle_data" is: -0.0683. This is roughly a .0038 difference from the "dino_data" correlation coefficient.

Plot of the circle dataset:

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
     filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
   geom_point()
```

And the calculated correlation coefficient:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x,y))
```

### Exercise 5
The summarized plots of all datasets in the datasauRus package:

```{r plot-summary}
ggplot(datasaurus_dozen,aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```

And the summarized correlation coefficients:

```{r cor-group}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r =cor(x, y)) %>%
  print(13)
```